Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-28 src/tex/intro.tex
Add comments and update abs/into/methods -- add o3b gaussian chieff to plot

Observations of gravitational waves (GWs) from compact binary coalescences (CBCs) is becoming a regular occurrence, 
recently producing catalogs of 90 such detection \cite{GWTC1,gwtc2,GWTC3}. With this growing catalog size, we are steadily approaching a more complete  
understanding of the population properties CBCs, just 7 years after the first observation \cite{o1o2_pop,o3a_pop,o3b_astro_dist}. 
In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration detectors \citep{aLIGO,aVIRGO}, with the increased sensitivities, 
there could be a detection as often as every day \cite{LVK_prospects}. This large influx of incoming data will drastically increase what we can learn by combining all observations
in order to studying the compact object population. The history of these dense objects is imprinted on the properties of the population 
of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitation radiation emitted. The population distibutions 
of merging compact objects inferred from gravitational-wave observations has been shown to be parituclar useful in order to, measure cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, 
constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2}, constrain a running Planck mass \citep{Lagos_runningPlanckMass}, look for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng}, 
constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, and constrain the neutron star equation of state \citep{Golomb_EOS}. 
Through a better understanding of the mass, spin, and redshift distributions of compact binaries that will come with the increased catalog size, 
one can probe a wide range of different physical phenoma with even greater fidelity.

Studies using flexible methods to analyze the binary black hole (BBH) mass distribution with GWTC-2 \citep{Tiwari_2021_b,Edelman_2022ApJ} found signs of structure 
beyond the reported $m_1\sim35\,\msun$ feature by \citet{Talbot_2018, o3a_pop}. The has evidence for this structure, such as the peak at $m_1\sim10\,\msun$, has only increased
with GWTC-3 \cite{o3b_astro_dist,Tiwari_2022ApJ}. This substructure was first confidently found with mutliple different flexible or non-parametric models that aim 
to be data-oriented with little bias on the functional form. Conversely the other canonical approach is to use simple parametric models that aim to describe the data
in the simplest way, building in astrophyscially motivated priors, followed by sequentially adding complexities only as the data demands it. While in the current environment 
this simple approach is clearly more powerful, as we go forward into the data-rich catalog era flexible models can be a useful complement.
Non-parametric or semi-parametric methods are particularly useful at looking for unexpected features in the data, or finding where 
our simpler parametric models may be missing features in the data. Development and robust teting of these types of methods in the short term will provide
knock dowm effects later down the line as the size of our catalogs increase and we enter a data-dominated regime rather than prior/model dominated.

The spin distributions of binary black holes (BBHs) have particular interest since the two main formation scenarios of BBHs produce 
distinctly different spin distrubitons \bruce{cite}. Isolated or field formation scenarios predict spins that are preferentially, although some small misalignment can occur 
depending on the nature of the supernovae kicks as each star collapses to a compact object \bruce{cite}. Dynamical formation scenarios occur in dense environments where 
many-body interactions between a large number compact objects occur before producing a binary that will merger within a Hubble time. Thus the dynamical channel produces 
an isotropic spin orientation distribution \bruce{cite}. It has also been of controversial interest in the literature recently, with different parameteric approaches finding 
different conclusions on the distribution of spins of BBHs. Recent studies have disagreed on the possible existence of a significant zero-spinning subpopulation, along with the 
presence of significant mis-alignment ($\cos{\theta_i} < 0.0$) \cite{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}. A recent study 
has shown the spin orientation distribution infernce is senitive to modeling choices and may not peak at perfectly aligned spins, as is commonly assumed \cite{spinitasyoulike}. 
Other approaches to building better models for BBH spins again, as with the mass models, focus on iterating through different simple parameteric descriptions with 
increasing complexities \cite{BuildBetterSpinModels,Callister_NoEvidence,spinitasyoulike}. The spin distributions offer a nice use case for flexible data-driven models, both 
to help alleivate the current disputes in the literature and because there has been little work on flexible model development for the spin distribution of BBHs thus far.

Polynomial splines have been applied to success across different areas of gravitational-wave astronomy. They have been used to model the gravitational-wave data noise spectrum, 
detector calibration uncertainties, coherent gravitational waveform deviations, and modulations to a power law mass distribution \cite{Littenberg_2015,Edwards_2018,B_Farr_etal_2014,Edelman_2021,Edelman_2022ApJ}
In this paper we highlight how the use of basis-splines can provide a powerful non-parametric modeling approach to the astrophysical distributions of compact 
binaries. We illustrate how one can efficiently model the mass and spin distributions of compact binaries in GWTC-3 with basis splines to infer population properties using 
hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and how this method complements the simpler lower dimensional parametric models. 
This data-drien approach will be capable of finding more subtle features, that may not be expected, should they appear in future catalogs. 
In Section \ref{sec:basis_splines} we go over the background of basis splines, in Section \ref{sec:results} we present results using our basis 
spline model on the mass and spin distributions of BBHs in GWTC-3, followed by discussing results in their astrophysical context Section \ref{sec:astrodiscussion} 
and concluding in Section \ref{sec:conclusion}.

>>>>

Observations of gravitational waves (GWs) from compact binary coalescences (CBCs) are becoming a regular occurrence, 
recently producing catalogs of 90 such detections \citep{GWTC1,gwtc2,GWTC3}. With this growing catalog size, we are steadily approaching a more complete  
understanding of the population properties of CBCs, just 7 years after the first observation \citep{o1o2_pop,o3a_pop,o3b_astro_dist}. 
In the coming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration detectors \citep{aLIGO,aVIRGO}, with the increased sensitivities, 
there could be a detection as often as every day \citep{LVK_prospects}. This large influx of incoming data will drastically increase what we can 
learn by combining all observations in order to study the compact object population. The history of these dense objects is imprinted on the properties 
of the population  of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitational radiation emitted \citep{Zevin_2017}. 
The population distributions of merging compact objects inferred from gravitational-wave observations have been shown to be particularly useful in order to
measure cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2}, 
constrain a running Planck mass \citep{Lagos_runningPlanckMass}, look for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng}, 
constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, 
and constrain the neutron star equation of state \citep{Golomb_EOS}. Through a better understanding of the mass, spin, and redshift distributions of 
compact binaries that will come with the increased catalog size, one can probe a wide range of different physical phenomena with even greater fidelity.

Studies using flexible methods to analyze the binary black hole (BBH) mass distribution with GWTC-2 found signs of structure 
beyond the first reported feature found at $m_1\sim35\,\msun$ \citep{Talbot_2018,o3a_pop,Tiwari_2021_b,Edelman_2022ApJ}. The evidence for this structure, 
such as the peak at $m_1\sim10\,\msun$, has only increased after analyzing the following catalog, GWTC-3 \citep{o3b_astro_dist,Tiwari_2022ApJ}. 
This substructure was first confidently found with multiple different flexible or non-parametric models that are data-driven with little 
bias on the functional form. Conversely, the other canonical approach is to use simple parametric models that aim to describe the data
in the simplest way, building in astrophysically motivated priors, followed by sequentially adding complexities only as the data demands it. While in data-scarce, prior dominated
environments, this simple approach is more powerful. However, as we go forward into the data-rich catalog era, flexible models will be necessary to discover new features that may be in
the data, which quickly becomes unwieldy with the sequential approach. Non-parametric or semi-parametric methods are particularly useful in looking for unexpected features in the data, finding where 
our simpler parametric models may be failing to capture meaningful features in the data. Development and robust testing of such methods in the short term will provide
knock on effects as the size of our catalogs increase, and GW astronomy enters its data-dominated era.

The spin distributions of BBHs are particularly interesting since the two main formation scenarios produce distinctly different spin distributions \bruce{cite}. 
Isolated or field formation scenarios predict component spins that are preferentially aligned with the binaries orbital angular momentum, although some small 
misalignment can occur depending on the nature of the supernova kicks as each star collapses to a compact object \bruce{cite}. Dynamical formation scenarios may 
occur in dense environments where many-body interactions between a large number compact objects occur during the binary formation hardening the binary so that it 
will merge within a Hubble time. Thus, the dynamical channel produces an isotropic spin tilt distribution \bruce{cite}. BBH spins have also been of controversial 
interest recently, with different parametric approaches to modeling the spin distribution coming to different conclusions. The studies have disagreed on the possible existence 
of a significant zero-spinning subpopulation, along with the presence of significant spin misalignment (i.e. $\cos{\theta_i} < 0.0$) \citep{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}. 
Another study recently showed that the spin tilt distribution inference is sensitive to modeling choices and may not peak at perfectly aligned spins, as is often assumed \citep{spinitasyoulike}. 
Other approaches to building improved models for BBH spins again, as with the mass models, focus on iterating through different simple parametric descriptions with 
increasing complexities \citep{BuildBetterSpinModels,Callister_NoEvidence,spinitasyoulike}. The spin distributions offer a nice use case for flexible data-driven models, as 
we present in this manuscript, both to help alleviate the current disputes in the literature and because there has been little work on flexible model development for the 
spin distribution of BBHs beyond assuming aligned spins thus far \citep{Tiwari_2021_a,Tiwari_2021_b}.

Polynomial splines have been applied to success across different areas of gravitational-wave astronomy. They have been used to model the gravitational-wave data noise spectrum, 
detector calibration uncertainties, coherent gravitational waveform deviations, and modulations to a power law mass distribution \citep{Littenberg_2015,Edwards_2018,B_Farr_etal_2014,Edelman_2021,Edelman_2022ApJ}
In this paper we highlight how the use of basis-splines can provide a powerful non-parametric modeling approach to the astrophysical distributions of compact 
binaries. We illustrate how one can efficiently model both the mass and spin distributions of merging compact binaries in GWTC-3 with basis splines to infer CBC population properties using 
hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and how this method complements the simpler lower 
dimensional parametric models in the short run, and will become necessary with future catalogs. This data-driven approach will provide checks of our understanding by finding more 
subtle features, that may not be expected, should they appear in with more observations. The rest of this manuscript is structured by first going over the background of basis splines in 
section \ref{sec:basis_splines}, followed by presenting the results of our extensive data-driven study of the mass and spin distributions of BBHs in GWTC-3 section \ref{sec:results}. We 
discuss our results and their astrophysical implications in section \ref{sec:astrodiscussion}, finishing with our conclusions in section \ref{sec:conclusion}.

### 2022-09-28 src/tex/methods.tex
move again...
Update methods.tex
change fig widths
fix latex figs
Add comments and update abs/into/methods -- add o3b gaussian chieff to plot

A common non-parametric method in used in many statistical applications is basis splines. A spline function of order $k$, 
is a piece-wise polynomial of order $k$ polynomials stitched together from defined ``knot'' locations across the domain. 
They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
Basis splines of order $k$ are a set of order $k$ polynomials that form a complete basis for any spline function of order $k$. 
Given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines basis components for a given knot vector 
using the Cox-de Boor recursion formula \cite{deBoor78}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:

@@

\noindent where $\omega_{i,k}$ is defined as:

@@

\noindent allowing one to build a basis of $i$ components that spans the vector space of order-$k$ spline functions interpolated 
from this knot vector. This is known as the ``B-Spline'' basis after it's inventor de Boor \cite{deBoor78}. The power of basis splines
comes from the fact that you only have to do the, somewhat expensive, interpolation once for each set of points you want to evaluate your
spline functions at. This allows for much quicker speeds since each evaluation of the spline function becomes a simpler operation that is just
a dot product of 2d matrix and 1d vector. This straightforward operation is also ideal for optimizations from the use GPU accelerators, 
enabling expensive markov chain monte carlo (MCMC) based analyses with hundreds of parameters. Basis splines can easily be generalized to 
their two-dimensional analog, producing tensor product basis splines that, with this computational advantange, allow for high fidelity
modeling of two-dimensional spline functions.

A similar basis, the M-Spline basis \citep{monotone_regression_splines}, has desirable properties when looking to model a probability density function, 
which is the goal of population inference. Namely, $M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. We now have
a useful basis that can represent all spline functions that are probability density functions given our array of knots. The M-Spline basis differs 
from B-Splines by the normalization factor:

@@

\begin{figure}[ht!]
    \script{spline_basis_plot.py}
        \includegraphics[width=0.45\textwidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing proper MSpline bases with 20 degrees of freedom and equal weights for each component.}
        \label{fig:spline_basis}
\end{figure}

\noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper. 
Figure \ref{fig:spline_basis} shows an example of a 3rd order M-Spline basis with 20 degrees of freedom and knots linearly spaced from 0 to 1.
Another important feature of basis splines is that under appropiate prior conditions, one can alleviate sensitivities to arbitrarily 
chosen prior specifications that splines commonly struggle with. We look to the use of penalized splines or P-Splines \cite{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}, 
that adds a smoothing penalty (or prior) based on the difference of basis spline coeficients. This allows one to much more denseley populate
the domain with knots without the worry of extra variance in the inferred spline functions. We discuss the smoothing prior in more detail 
in Appendix \ref{sec:psplines}, along with our specific prior and basis choices for each model in Appendix \ref{sec:modelpriors}.

>>>>

A common non-parametric method used in many statistical applications is basis splines. A spline function of order $k$, 
is a piece-wise polynomial of order $k$ polynomials stitched together from defined ``knot'' locations across the domain. 
They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
\it{Basis splines} (or ``B-Splines'') of order $k$ are a set of order $k$ polynomials that form a complete basis for any spline function of order $k$. 
Therefore, given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
every possible spline function interpolated by knots, $\mathbf{t}$. The basis components for a given knot vector are constructed  
using the Cox-de Boor recursion formula \citep{deBoor78}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing a ``proper'' (see appendix \ref{sec:psplines}) M-Spline basis of order 3 (cubic) with 20 degrees of freedom and equal weights for each component. 
        In black, we show the resulting spline function with given equal weights and denote the location of the knots with gray x's.}
        \label{fig:spline_basis}
    \end{centering}
    \script{spline_basis_plot.py}
\end{figure}

@@

\noindent where above $\omega_{i,k}$ is defined as:

@@

\noindent This is known as the ``B-Spline'' basis after it's inventor de Boor \citep{deBoor78}. The power of basis splines
comes from the fact that one only has to do the somewhat-expensive interpolation once for each set of points at which the spline is evaluated. 
This provides a considerable computational speedup since each evaluation of the spline function becomes a simpler operation that is just
a dot product of a matrix and a vector. This straightforward operation is also ideal for optimizations from the use GPU accelerators, 
enabling expensive Markov chain Monte Carlo (MCMC) based analyses with hundreds of parameters \bruce{citation?}. 
Basis splines can easily be generalized to their two-dimensional analog, producing tensor product basis splines that, 
with this computational advantage, allow for high fidelity modeling of two-dimensional spline functions.

A similar basis, the M-Spline basis \citep{monotone_regression_splines}, has desirable properties when looking to model a probability density function, 
which is the goal of population inference. Each basis component is scaled such that it is normalized over the domain, $\int M_i(x)dx = 1$. This ensures 
that given a vector of basis coefficients, if they sum to unity, the resulting spline function is normalized across the interpolation domain. 
The M-Spline basis differs from B-Splines by the scaling factor that normalizes each component:

@@

\noindent We use this definition of the M-Spline basis for all the basis spline models used in this manuscript. Figure \ref{fig:spline_basis} 
shows an example of a cubic (3rd order) M-Spline basis with 20 degrees of freedom and knots linearly spaced from 0 to 1.
Another important feature of basis splines is that under appropriate prior conditions, one can alleviate sensitivities to arbitrarily 
chosen prior specifications that splines commonly struggle with. We look to the use of penalized splines (or P-Splines) \citep{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}, 
where one adds a smoothing prior based on the difference of basis spline coefficients. This allows one to populate the domain with more dense knots 
without the worry of extra variance in the inferred spline functions. We discuss the details of our smoothing prior implementation 
in more detail in Appendix \ref{sec:psplines}, along with our specific prior and basis choices for each model in Appendix \ref{sec:modelpriors}.

### 2022-09-28 src/tex/ms.tex
Add comments and update abs/into/methods -- add o3b gaussian chieff to plot

\begin{abstract}                 
We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical distribution of 
binary black hole (BBH) masses and spins using the 69 confident observations in GWTC-3. We report the same features previously recovered 
with similarly flexible models in the mass distribution, most notably the peaks in merger rates at \~10\msun and \~35\msun. 
We then use our method as the first non-parametric model applied to the BBH spin distribution, corroborating the results of \citet{spinitasyoulike}, 
showing that tilt distributions may not peak at $\cos(\theta_i) = 1$ as previous models assumed. We find broad agreement with the 
accepted conlcusions of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
and there is mild support for a non-spinning subpopulaton, but cannot resolve this with current catalog sizes. We also test components whether the data 
prefers the spin distributions to be identical for each component, finding no strong sign of differening distibutions. When modeling the $\chi_\mathrm{eff}$ 
distribution with basis splines we find similar conclusions as previously reported, consistent with a non-isotropic distribution 
(peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}), showing considerable support 
($f_{\chi_\mathrm{eff}<0}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
We conclude by discussing how non-parametric methods in gravitatonal-wave population inference are poised to provide a useful complement to 
the usual parametric approach going into the data rich catalog era of gravitational-wave astronomy.
\end{abstract}

@@

\section{Acknowledgements}\label{sec:acknowledments}
We thank Will Farr, Tom Callister, Amanda Farah and Maya Fishbach for useful discussions during the preparation this manuscript, 
along with helpful comments on an early draft by Tom Callister.
This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
The authors are grateful for computational resources provided by the LIGO Laboratory and supported by National Science Foundation Grants PHY-0757058 and PHY-0823459.  
This work benefited from access to the University of Oregon high performance computer, Talapas. This material is based upon work supported 
in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
fully funded by the National Science Foundation.
\software{
\textsc{Astropy}~\citep{2018AJ....156..123A},
\textsc{NumPy}~\citep{harris2020array},
\textsc{Matplotlib}~\citep{Hunter:2007},
\textsc{Jax}~\citep{jax},
\textsc{NumPyro}~\citep{pyro,numpyro},
\textsc{GWPopulation}~\citep{Talbot_2019},
\textsc{Bilby}~\citep{Ashton_2019,bilby_gwtc1},
\textsc{Dynesty}~\citep{Speagle_2020}
}
\bibliography{bib}{}
\bibliographystyle{aasjournal}

>>>>

\begin{abstract}                 
We introduce a non-parametric model built from basis splines, and use it to infer the astrophysical distribution of 
binary black hole (BBH) masses and spins using the 69 confident observations in GWTC-3, in the most comprehensive data-driven
investigation of the compact object population. We report the same features previously recovered 
with similarly flexible models focusing solely on the mass distribution, most notably the peaks in merger rates at $\sim10\msun$ and $\sim35\msun$. 
Our study provides the first non-parametric investigation into BBH spin distribution, while simultaneously modeling the mass distribution in the same way, 
showing signs that the spin tilt distributions may not peak at $\cos(\theta_i) = 1$ as previous models assumed. We find broad agreement with the 
accepted conclusions of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
and there is mild support for a non-spinning subpopulation, which may become resolvable with larger catalogs. 
We also perform a data-driven test of whether the data prefers the spin distributions to be identical for both the more and less massive binary components, 
finding no strong sign of differing distributions. When modeling the $\chi_\mathrm{eff}$ distribution with our model we find similar 
conclusions as previously reported, the distribution is consistent with a non-isotropic distribution (that peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}), 
showing considerable support ($f_{\chi_\mathrm{eff}<0}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
We conclude by discussing how non-parametric methods in gravitational-wave population inference are poised to provide a useful complement to 
the parametric approach going into the data-rich catalog era of gravitational-wave astronomy.
\end{abstract}

@@

\section{Acknowledgements}\label{sec:acknowledments}
We thank Will Farr, Tom Callister, Amanda Farah and Maya Fishbach for useful discussions during the preparation this manuscript, 
along with helpful comments on an early draft by Tom Callister.
This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
The authors are grateful for computational resources provided by the LIGO Laboratory and supported by National Science Foundation Grants PHY-0757058 and PHY-0823459.  
This work benefited from access to the University of Oregon high performance computer, Talapas. This material is based upon work supported 
in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF's LIGO Laboratory which is a major facility 
fully funded by the National Science Foundation.
\software{
\textsc{Astropy}~\citep{2018AJ....156..123A},
\textsc{NumPy}~\citep{harris2020array},
\textsc{Matplotlib}~\citep{Hunter:2007},
\textsc{Jax}~\citep{jax},
\textsc{NumPyro}~\citep{pyro,numpyro},
\textsc{GWPopulation}~\citep{Talbot_2019},
\textsc{Bilby}~\citep{Ashton_2019,bilby_gwtc1},
\textsc{Dynesty}~\citep{Speagle_2020}
}
\bibliography{bib}{}
\bibliographystyle{aasjournal}
